---
title: "Reproducibility example: Birds"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
```

## Introduction

Here I am practicing making an R Markdown. I will be using data from birds.csv for this document.

```{r code_block1}
#Load in birds data
library(readr)
birds <- read_csv("data/birds.csv")
```

## Plotting size relationships

```{r}
ggplot(birds, aes(birds$Tarsus.Length, birds$Wing.Length)) + geom_point() + xlab('Tarsus Length') + ylab('Wing Length')
```

Here we have plotted tarsus length against wing length. In this plot, we can see there is a general positive correlation between tarsus and wing lengths. However, there several individuals with a tarsus length between 50-100 and a wing length near 0, as well as several with a tarsus length > 400 and a dispraportionately small wing length.

```{r}
birds %>%
  filter(Tarsus.Length > 400) %>%
  select(Species2_eBird, Tarsus.Length, Wing.Length) %>%
  group_by(Species2_eBird) %>%
  tally() %>%
  print()
```
There are several outliers within this dataset. The code above will select the outliers with a large Tarsus length and small Wing length.

```{r}
birds %>%
  filter(Wing.Length < 10) %>%
  select(Species2_eBird, Tarsus.Length, Wing.Length) %>%
  group_by(Species2_eBird) %>%
  tally() %>%
  print()
```
The code above will identify outliers with a small tarsus length and a very small wing length.


## Write a function

To convert phenotypic measurements from mm to cm we can use the following function:
```{r}
convert <- function(x){
  z = x/10
  return(z)
}
birds_cm <- convert(birds[,14:23])
```


## Some bird queries

```{r}
birds %>%
  filter(Beak.Length_Culmen == max(birds$Beak.Length_Culmen, na.rm = TRUE)) %>%
  select(Species2_eBird, Beak.Length_Culmen, Beak.Length_Nares) %>%
  print()
```

```{r}
birds %>%
  filter(Beak.Length_Nares == max(birds$Beak.Length_Nares, na.rm = TRUE)) %>%
  select(Species2_eBird, Beak.Length_Culmen, Beak.Length_Nares) %>%
  print()
```

Pelecanus Conspicillatus has the longest beak. This is true both when measuring from the culmen or from the nares.

## Crows, ravens and magpies

```{r}
birds %>%
  filter(Species2_eBird == 'Corvus corone' | Species2_eBird == 'Corvus corax' | Species2_eBird == 'Pica pica') %>%
  ggplot(aes(Species2_eBird, Beak.Depth)) + geom_boxplot() + xlab('Species') + ylab('Beak Depth')
```

```{r}
birds %>%
  filter(Species2_eBird == 'Corvus corone' | Species2_eBird == 'Corvus corax' | Species2_eBird == 'Pica pica') %>%
  ggplot(aes(Species2_eBird, Beak.Length_Culmen)) + geom_boxplot() + xlab('Species') + ylab('Beak Length')
```

The above boxplots will display the distributon of beak depth and lengths among crows, ravens an magpies. Here we can see that Crows have both the largest beak depth and length.